The Privacy of Private Browsing

### 2013-12-11 finalproject/paper.tex
removed revised sections

\documentclass[pdftex,letterpaper,titlepage,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{array}

@@

  \begin{abstract}
  Eventually the abstract will go here.
  \end{abstract}

  \section{Introduction}
    \subsection{Browser Overview}
    The following table summarizes the web browsers that will be considered in
    this paper. The features that a particular web browser's private mode is
    believed to have comes from the developers of the browser. Note that all
    browsers run on both Windows and Linux, with the exception of Internet
    Explorer, which runs only on Windows.\cite{verdi13}\cite{google13}
    \cite{ie13}

    \begin{center}
      \begin{tabular}{|m{'5cm'}|c|c|c|}
        \hline
        Property & Mozilla Firefox & Google Chrome & Internet Explorer \\
        \hline
        Browser history & X & X & X \\
        \hline
        Form data & X &  & X \\
        \hline
        Search bar data & X &  & X \\
        \hline
        Passwords & X &  & X \\
        \hline
        Downloads & X & X &  \\
        \hline
        Cookies & X & X & X \\
        \hline
        Cached files & X &  & X \\
        \hline
        Simulataneous sessions with different privacy settings & X & X & X \\
        \hline
        Hides activity from ISP &  &  &  \\
        \hline
        Hides activity from websites &  &  &  \\
        \hline
      \end{tabular}
    \end{center}

  This paper also discusses the Tor browser. Unlike Firefox, Chrome, and
  Internet Explorer, the Tor browser connects users to the internet using the
  Tor network. This does much more to preserve browsing anonymity than the
  browsers listed above. TODO finish this\ldots lazy.

  Most modern web browsers offer some sort of private browsing mode. This is
  supposed to allow users to view web content without other users of the same
  computer being able to determine what websites were visited. What is kept
  private and what is not differs from browser to browser. An overview of the
  most common browsers for Windows and Linux is provided below.

@@

    \subsection{Tor Browser Bundle}
    The Tor Browser Bundle runs on both Windows and Linux.

>>>>

\documentclass[pdftex,letterpaper,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

@@

  \begin{abstract}
  %write this
  \end{abstract}

  \section{Introduction}
    \subsection{Browser Overview}
    Currently, the most popular browsers for the Windows and Linux families of
    operating systems are Mozilla Firefox, Google Chrome, and Microsoft 
    Internet Explorer. (Internet Explorer runs only on the Windows family of
    operating systems, whereas Firefox and Chrome run on both Windows and 
    Linux.) All three of these browsers have built-in private browsing modes.
    The features and protections provided by each of these private browsing
    modes are summarized below.\cite{verdi13}\cite{google13}\cite{ie13}

    \begin{center}
      \begin{tabular}{|p{5cm}|c|c|c|}
        \hline
         & Firefox & Chrome & Internet Explorer \\
         & Private Browsing & Incognito Mode & InPrivate Browsng \\
        \hline
        Browser history & X & X & X \\
        \hline
        Form data & X &  & X \\
        \hline
        Search bar data & X &  & X \\
        \hline
        Passwords & X &  & X \\
        \hline
        Downloads & X & X &  \\
        \hline
        Cookies & X & X & X \\
        \hline
        Cached files & X &  & X \\
        \hline
        Simulataneous sessions with different privacy settings & X & X & X \\
        \hline
        Hides activity from ISP &  &  &  \\
        \hline
        Hides activity from websites &  &  &  \\
        \hline
      \end{tabular}
    \end{center}

    This paper also discusses the Tor browser. Unlike Firefox, Chrome, and
    Internet Explorer, the Tor browser connects users to the internet using the
    Tor network. This does much more to preserve browsing anonymity than the
    browsers listed above. %finish this section

    \subsection{Known Issues with Private Browsing}
    Prior research in this area indicates that web browsers, even when used in
    their respective private browsing modes, can leave artifacts on a user's
    machine that can reveal their internet activities. %finish

  % Remove below before final submission
  \iffalse
  Most modern web browsers offer some sort of private browsing mode. This is
  supposed to allow users to view web content without other users of the same
  computer being able to determine what websites were visited. What is kept
  private and what is not differs from browser to browser. An overview of the
  most common browsers for Windows and Linux is provided below.

@@

    \subsection{Tor Browser Bundle}
    The Tor Browser Bundle runs on both Windows and Linux. 
  \fi
